%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{6.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Robert Hitt} % Your name at the top
 
\moveleft.5\hoffset\centerline{Amissville, Virginia $\bullet$ (703) 895-1923 $\bullet$ rhitt@gmu.edu}
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt} % Horizontal line after name; adjust line thickness by changing the '1pt'

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%---------------------------------------------------------------------------------------- 

\vspace{-18pt}\section{EXPERIENCE}
{Software Engineering Intern, \sl Data Works Inc.} \hfill May 2017 - July 2017 \smallskip
\begin{itemize}
\item Worked with 4 other interns to develop a data triage tool that allows organizations to get a high level understanding of what types of data are in their backlog and prioritize that data for analysis without manual inspection. 
\item The project focused on developing a classification system capable of identifying specific attributes (i.e. names, phone numbers, email addresses, monetary data, etc.) and using these characteristics to score the data's relevance/importance.
\end{itemize} 
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

{\sl Bachelor of Computer Science,}  \hfill August 2016 - June 2018 \\
George Mason University, Fairfax, VA \hfill GPA: 3.41/4.00 \smallskip\\
Relevant Courses: Data Structures, Linear Algebra, Probability and Statistics

{\sl Associate of Computer Science,}  \hfill August 2014 - June 2016 \\
Northern Virginia Community College, Annandale, VA \hfill GPA: 3.33/4.00 \smallskip\\
Graduated Cum Laude
 
%----------------------------------------------------------------------------------------
%	Technology SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{TECHNOLOGY SKILLS} 

{\sl Programming Languages:} \\ \null\qquad - Python, Kotlin, Java, Javascript, Clojure, C \smallskip\\
{\sl Frameworks:} \\ \null\qquad - Apache Spark, Angular 4, Elasticsearch, JUnit \smallskip\\
{\sl Software/Operating Systems:} \\ \null\qquad - Git, Linux, Vim, VSCode, Android, Windows
 
%----------------------------------------------------------------------------------------
%	ACTIVITES SECTION
%----------------------------------------------------------------------------------------
 
\section{ACTIVITIES}

{\sl Mason Student Run Computing \& Technology} \hfill August 2016 - Present
\begin{itemize}
\item Coordinated and mentored in hackathons and workshops introducing other students to subjects such as Git version control and contributing to open source software.
\item Managed and contributed to various open source projects designed to benefit George Mason students.
\end{itemize} 

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\section{PROJECTS} 

What's Open
\begin{itemize}
\item Project lead and active contributor to Android app which displays George Mason University facility data from an HTTP API and presents what facilities on campus are open and those facilities' schedules.
\end{itemize}

Iodine Monoxide
\begin{itemize}
\item Project developed for HackNC 2016. Unity app that allows students to model chemical structures with Leap Motion devices and concurrently displays those models in a Heroku web app.
\item Won first place at HackNC 2016.
\end{itemize}

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}
