%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

% !TEX program = lualatex
% ^ magic which gives VSCode's LaTeX plugin the correct typesetting engine

\documentclass[11pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
\usepackage{fontspec}

\defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
\topmargin=-0.6in  % start text higher on the page
\setlength{\textheight}{10in} % increase text height to fit resume on 1 page
\newsectionwidth{0pt}  % So the text is not indented under section headings
\renewcommand{\labelitemii}{$\circ$} % change second-level list symbols to hollow bullets

\usepackage[left=1.5cm, right=1.5cm, top=1cm, bottom=0cm]{geometry}

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Robert Hitt} % Your name at the top

\moveleft.5\hoffset\centerline{Fairfax, Virginia  $\bullet$  (703) 895-1923  $\bullet$  rhitt@gmu.edu  $\bullet$  github.com/roberthitt}

\vspace{-15pt}
\noindent\makebox[\linewidth]{\rule{\textwidth}{1pt}}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	Technology SKILLS SECTION
%----------------------------------------------------------------------------------------

\vspace{-26pt}\section{\LARGE Skills} \smallskip

\textbf{Programming Languages:} Python, Java, SQL, Javascript, Kotlin, C \smallskip\\
\textbf{Frameworks:} Angular, React, Scikit-learn, Apache Spark, Android \smallskip\\
\textbf{Software/Operating Systems:} Git, Linux, Oracle, Docker, Visual Studio Code, Vim

\vspace{-15pt}
\noindent\makebox[\linewidth]{\rule{\textwidth}{1pt}}

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\vspace{-10pt}\section{\LARGE\bf Experience} \smallskip

\textbf{Undergraduate Research Assistant} \hfill May 2018 - Present \\
George Mason University\smallskip
\begin{itemize}
\item Work with multi-disciplinary team on research topics primarily focused on development of autonomous vehicles.
\item Developed Angular 6 application for annotating video datasets.
\item Trained deep learning models on hand-labelled video datasets for object detection.
\end{itemize}

\vspace{-8pt}\textbf{Computer Science Teaching Assistant} \hfill January 2018 - Present \\
George Mason University\smallskip
\begin{itemize}
\item Answer students' questions on university's online Q\&A board.
\item Assist and instruct students during Systems Programming labs.
\item Periodically assist graduate students with grading lab work.
\end{itemize}

\vspace{-8pt}\textbf{Software Development Intern} \hfill May 2017 - July 2017 \\
Data Works Inc.\smallskip
\begin{itemize}
\item Worked with a team of interns to develop a data analysis tool that allows organizations to categorize large datasets without manual inspection.
\item Developed Apache Spark modules for data extraction, generated data for training deep learning models, and developed Angular frontend components.
\end{itemize}

\vspace{-15pt}
\noindent\makebox[\linewidth]{\rule{\textwidth}{1pt}}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\vspace{-10pt}\section{\LARGE Projects} \smallskip

\textbf{What's Open} -- git.gmu.edu/srct/whats-open-android \smallskip
\begin{itemize}
\item Android app which pulls George Mason University facility data from an API and displays the open status and schedules of campus facilities, with optional notifications.
\end{itemize}

\vspace{-8pt}\textbf{Iodine Monoxide} -- devpost.com/software/leap-motion-classroom-tool \smallskip
\begin{itemize}
\item Won first place at HackNC 2016.
\item Unity app that allows students to model chemical structures with Leap Motion devices and concurrently display those models in a Flask web app.
\end{itemize}

\vspace{-15pt}
\noindent\makebox[\linewidth]{\rule{\textwidth}{1pt}}

%----------------------------------------------------------------------------------------
%	ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\vspace{-10pt}\section{\LARGE Activities} \smallskip

\textbf{Vice President}, Mason Student Run Computing \& Technology \hfill August 2016 - Present\smallskip
\begin{itemize}
\item Coordinate and mentor hackathons and workshops that introduce other students to subjects such as Git version control and making contributions to open source software.
\item Manage and contribute to various open source projects intended to benefit Mason students.
\item Submit budget requests to reserve funding for organization-run events.
\end{itemize}

\vspace{-15pt}
\noindent\makebox[\linewidth]{\rule{\textwidth}{1pt}}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\vspace{-10pt}\section{\LARGE Education} \smallskip

\textbf{Bachelor of Computer Science}  \hfill August 2016 - Present\\
\medskip
George Mason University, Fairfax, VA \hfill GPA: 3.51/4.00\\
\textbf{Relevant Courses:} Data Mining, Software Engineering, Database Concepts\\
\textbf{Expected Graduation Date:} May 2019

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}
